15th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-07 rules/rules21.tex
updating divisions with new logics

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2021.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2021 are designed to not overly punish solvers producing
syntactically wrong output, by treating those outputs as unknown and
not as unsoundness.  Moreover, we added more divisions to the model
validation track.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf \maintrack.} Previously, every logic in the \maintrack was its own
  division.  There are currently over 60 logics in SMT-LIB, which makes a short
  summary of the results impossible.  On the other hand the competition-wide
  scoring does a comparison between solvers that cannot be sensibly compared as
  they support completely disjoint logics. To get a better overview, this year
  we have in the \maintrack divisions combining related logics, thus reducing
  the number of divisions and obtaining more manageable and meaningful results.
  Rather than logics, solvers will declare the divisions they enter in the
  \maintrack. They will be ranked by the number of benchmarks they solve across
  all logics in the divisions entered.
  \begin{itemize}
    \item Quantifier-free divisions:
    \begin{itemize}
      \item QF\_Equality\\
Logics: QF\_UF, QF\_AX, QF\_DT
\item QF\_Equality+LinearArith\\
Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
\item QF\_Equality+NonLinearArith\\
Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
\item QF\_Equality+BVArith\\
Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
\item QF\_LinearIntArith\\
Logics: QF\_LIA, QF\_LIRA, QF\_IDL
\item QF\_LinearRealArith\\
Logics: QF\_LRA, QF\_RDL
\item QF\_BV
\item QF\_FPArith\\
Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_BVFPLRA, QF\_ABVFPLRA
\item QF\_NonLinearIntArith\\
Logics: QF\_NIA, QF\_NIRA
\item QF\_NRA
\item QF\_Strings\\
Logics: QF\_S, QF\_SLIA

    \end{itemize}
    \item Divisions with quantifiers:
    \begin{itemize}
      \item Equality\\
Logics: UF, UFDT
\item Equality+LinearArith\\
Logics: ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
\item Equality+MachineArith\\
Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, UFBV, AUFBVDTLIA
\item Equality+NonLinearArith\\
Logics: AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA
\item Arith\\
Logics: LRA, LIA, NIA, NRA
\item BV
\item FPArith\\
Logics: BVFP, FP, BVFPLRA, FPLRA
    \end{itemize}
  \end{itemize}

>>>>

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2021.
%
As in previous years, we have revised the rules slightly.  Some rule
changes in 2021 are designed to not overly punish solvers producing
syntactically wrong output, by treating those outputs as unknown and
not as unsoundness.  Moreover, we added more divisions to the model
validation track.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf \maintrack.} Previously, every logic in the \maintrack was its own
  division.  There are currently over 60 logics in SMT-LIB, which makes a short
  summary of the results impossible.  On the other hand the competition-wide
  scoring does a comparison between solvers that cannot be sensibly compared as
  they support completely disjoint logics. To get a better overview, this year
  we have in the \maintrack divisions combining related logics, thus reducing
  the number of divisions and obtaining more manageable and meaningful results.
  Rather than logics, solvers will declare the divisions they enter in the
  \maintrack. They will be ranked by the number of benchmarks they solve across
  all logics in the divisions entered.
  \begin{itemize}
    \item Quantifier-free divisions:
    \begin{itemize}
      \item QF\_Equality\\
Logics: QF\_UF, QF\_AX, QF\_DT, QF\_UFDT
\item QF\_Equality+LinearArith\\
Logics: QF\_ALIA, QF\_AUFLIA, QF\_UFLIA, QF\_UFLRA, QF\_UFIDL
\item QF\_Equality+NonLinearArith\\
Logics: QF\_UFNRA, QF\_UFNIA, QF\_ANIA, QF\_AUFNIA
\item QF\_Equality+Bitvec\\
Logics: QF\_ABV, QF\_UFBV, QF\_AUFBV
\item QF\_Equality+Bitvec+Arith\\
Logics: QF\_AUFBVLIA, QF\_AUFBVNIA, QF\_UFBVLIA
\item QF\_LinearIntArith\\
Logics: QF\_LIA, QF\_LIRA, QF\_IDL
\item QF\_LinearRealArith\\
Logics: QF\_LRA, QF\_RDL
\item QF\_Bitvec\\
Logics: QF\_BV
\item QF\_FPArith\\
Logics: QF\_FP, QF\_UFFP, QF\_FPLRA, QF\_BVFP, QF\_ABVFP, QF\_AUFBVFP, QF\_BVFPLRA, QF\_ABVFPLRA
\item QF\_NonLinearIntArith\\
Logics: QF\_NIA, QF\_NIRA
\item QF\_NonLinearRealArith\\
Logics: QF\_NRA
\item QF\_Strings\\
Logics: QF\_S, QF\_SLIA, QF\_SNIA

    \end{itemize}
    \item Divisions with quantifiers:
    \begin{itemize}
      \item Equality\\
Logics: UF, UFDT
\item Equality+LinearArith\\
Logics: ALIA, AUFLIA, UFLIA, UFIDL, AUFLIRA, UFLRA, UFDTLIA, UFDTLIRA, AUFDTLIA, AUFDTLIRA
\item Equality+MachineArith\\
Logics: AUFFPDTLIRA, UFFPDTLIRA, UFFPDTNIRA, ABVFP, ABVFPLRA, AUFBV, AUFBVFP,
AUFBVDTLIA, UFBV, UFBVFP, UFBVLIA
\item Equality+NonLinearArith\\
Logics: ANIA, AUFDTNIRA, UFDTNIA, UFDTNIRA, AUFNIA, AUFNIRA, UFNIA, UFNRA
\item Arith\\
Logics: LRA, LIA, NIA, NRA
\item Bitvec\\
Logics: BV
\item FPArith\\
Logics: BVFP, FP, BVFPLRA, FPLRA
    \end{itemize}
  \end{itemize}
